Response to reviewers

### 2022-05-10 paper/paper-jsdse/paper-jsdse.tex
DC done with all her changes

This paper has illustrated the steps and decisions made to take a particular open data set and make it a textbook data set, ready for the classroom or research. In the first stage, we showed the steps performed to get the data from the NLSY79 database. The data format was converted to a tidy format for more flexibility in cleaning and exploring. Initial data analysis was conducted to investigate and screen the quality of the data. We found and provided a fix for many anomalous observations in wages using a robust linear regression model. The refreshed data is compared with the original set using a variety of numerical summaries and graphics. The current subset is made available in a new R package, called \texttt{yowie}.

@@

\begin{itemize}
\tightlist
\item
  It primarily illustrates the steps in cleaning and processing a well-known longitudinal data so that it can be further refreshed as a textbook data set as new data emerges. Choices made during the cleaning and processing can affect findings made with the data, are transparent, and can be a basis for classroom discussions.
\item
  Some of the methods shown, and lessons learned about the data, can also be considered generally for data cleaning, initial data analysis and exploratory data analysis, useful for working with other data sets.
\item
  The refreshed data can be used for teaching advanced linear modeling, using almost identical code from Singer and Willett (2003), and thus make those lessons more current in time.
\item
  It provides the data to develop a case study for teaching exploratory data analysis of longitudinal data, focusing on the individual experience. The vignettes of the \texttt{brolgar} (Tierney, Cook, and Prvan 2020) package provide useful guides for the case study content.
\end{itemize}

>>>>

Any longitudinal dataset used for education should have a sufficiently reproducible process to be updated with new data. The NLSY79 dataset is a great teaching tool that has become outdated, both because the dataset stops in 1994, and because the demographic data could be handled more delicately. This paper has illustrated the necessary steps and decisions made to take a particular open data set and make it a textbook data set, ready for the classroom or research. In the first stage, we showed the steps performed to get the data from the NLSY79 database. The data format was converted to a tidy format for more flexibility in cleaning and exploring. Initial data analysis was conducted to investigate and screen the quality of the data. We found and provided a fix for many anomalous observations in wages using a robust linear regression model. The refreshed data is compared with the original set using a variety of numerical summaries and graphics. The current subset is made available in a new R package, called \texttt{yowie}.

@@

\begin{itemize}
\tightlist
\item
  It primarily illustrates the steps in cleaning and processing a well-known longitudinal data so that it can be further refreshed as a textbook data set as new data emerges. Choices made during the cleaning and processing can affect findings made with the data, are transparent, and can be a basis for classroom discussions.
\item
  Some of the methods shown, and lessons learned about the data, can also be considered generally for data cleaning, initial data analysis and exploratory data analysis, useful for working with other data sets.
\item
  The refreshed data can be used for teaching advanced linear modeling, using almost identical code from Singer and Willett (2003), and thus make those lessons more current for today's students.
\item
  It provides the data to develop a case study for teaching exploratory data analysis of longitudinal data, focusing on the individual experience. The vignettes of the \texttt{brolgar} (Tierney, Cook, and Prvan 2020) package provide useful guides for the case study content.
\end{itemize}

### 2022-05-10 paper/paper.Rmd
DC done with all her changes

This paper has illustrated the steps and decisions made to take a particular open data set and make it a textbook data set, ready for the classroom or research. In the first stage, we showed the steps performed to get the data from the NLSY79 database. The data format was converted to a tidy format for more flexibility in cleaning and exploring. Initial data analysis was conducted to investigate and screen the quality of the data. We found and provided a fix for many anomalous observations in wages using a robust linear regression model. The refreshed data is compared with the original set using a variety of numerical summaries and graphics. The current subset is made available in a new R package, called `r yowie`.

@@

- It primarily illustrates the steps in cleaning and processing a well-known longitudinal data so that it can be further refreshed as a textbook data set as new data emerges. Choices made during the cleaning and processing can affect findings made with the data, are transparent, and can be a basis for classroom discussions.
- Some of the methods shown, and lessons learned about the data, can also be considered generally for data cleaning, initial data analysis and exploratory data analysis, useful for working with other data sets.
- The refreshed data can be used for teaching advanced linear modeling, using almost identical code from @SingerJudithD2003Alda, and thus make those lessons more current in time.
- It provides the data to develop a case study for teaching exploratory data analysis of longitudinal data, focusing on the individual experience. The vignettes of the `brolgar` [@brolgar] package provide useful guides for the case study content.

>>>>

Any longitudinal dataset used for education should have a sufficiently reproducible process to be updated with new data.  The NLSY79 dataset is a great teaching tool that has become outdated, both because the dataset stops in 1994, and because the demographic data could be handled more delicately. This paper has illustrated the necessary steps and decisions made to take a particular open data set and make it a textbook data set, ready for the classroom or research. In the first stage, we showed the steps performed to get the data from the NLSY79 database. The data format was converted to a tidy format for more flexibility in cleaning and exploring. Initial data analysis was conducted to investigate and screen the quality of the data. We found and provided a fix for many anomalous observations in wages using a robust linear regression model. The refreshed data is compared with the original set using a variety of numerical summaries and graphics. The current subset is made available in a new R package, called `r yowie`.

@@

- It primarily illustrates the steps in cleaning and processing a well-known longitudinal data so that it can be further refreshed as a textbook data set as new data emerges. Choices made during the cleaning and processing can affect findings made with the data, are transparent, and can be a basis for classroom discussions.
- Some of the methods shown, and lessons learned about the data, can also be considered generally for data cleaning, initial data analysis and exploratory data analysis, useful for working with other data sets.
- The refreshed data can be used for teaching advanced linear modeling, using almost identical code from @SingerJudithD2003Alda, and thus make those lessons more current for today's students.
- It provides the data to develop a case study for teaching exploratory data analysis of longitudinal data, focusing on the individual experience. The vignettes of the `brolgar` [@brolgar] package provide useful guides for the case study content.

### 2022-05-10 response/response2.Rmd
update of intro according to AE comment
DC done with all her changes

XXX DC to do

@@

We think it is best to keep this emphasis, because the hard work is on cleaning and tidying the data, in a reproducible manner, which is close to the mission of the special issue. We have added some additional sentences about lessons for statistics and data science educators. XXX DC to do (might need help from Emi or Nick)

@@

Thanks for this, exactly right! We have changed the wording accordingly. XXX DC

@@

XXX DC to address

>>>>

We have revised the introduction to fix this. XXX DONE

@@

We have added additional bullet points on the benefit for educators in Section 5, in response to the overview comments by the Editor and AE (top of this response). We think it is best to keep content on cleaning and tidying the data, in a reproducible manner, to match the mission of the special issue. XXX DONE

@@

Thanks for this, exactly right! We have changed the wording accordingly, in various places in the paper. XXX DC, ET, NT please check that this message comes across clearly enough.

@@

See response above to the associate editor, about this concern. XXX DONE
